{\em Global} MILP models and PCA for \\ {\em real-time} DNN robustness certification

### 2025-11-15 CAV 2026/CAV2026_main.tex
abstract and title

\usepackage{times}  % DO NOT CHANGE THIS
\usepackage{helvet}  % DO NOT CHANGE THIS
\usepackage{courier}  % DO NOT CHANGE THIS
\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS
\urlstyle{rm} % DO NOT CHANGE THIS
\def\UrlFont{\rm}  % DO NOT CHANGE THIS
\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\frenchspacing  % DO NOT CHANGE THIS
\setlength{\pdfpagewidth}{8.5in} % DO NOT CHANGE THIS
\setlength{\pdfpageheight}{11in} % DO NOT CHANGE THIS
%
% These are recommended to typeset algorithms but not required. See the subsubsection on algorithms. Remove them if you don't have algorithms in your paper.
\usepackage{algorithm}
\usepackage{algorithmic}
\pagestyle{plain}
\usepackage{threeparttable}
\input{math_commands.tex}
\usepackage{lineno}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{cases}
\captionsetup{compatibility=false}
\usepackage{epstopdf}
\usepackage{placeins}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{calc}
\usepackage{array}
%\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usetikzlibrary{positioning, arrows.meta,calc}
\usepackage{newfloat}
\usepackage{listings}
\DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} % DO NOT CHANGE THIS
\lstset{%
	basicstyle={\footnotesize\ttfamily},% footnotesize acceptable for monospace
	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,% show line numbers, remove this entire line if you don't want the numbers.
	aboveskip=0pt,belowskip=0pt,%
	showstringspaces=false,tabsize=2,breaklines=true}
\floatstyle{ruled}
\newfloat{listing}{tb}{lst}{}
\floatname{listing}{Listing}
%\newtheorem{proposition}{Proposition}
%\newtheorem{definition}{Definition}
\newcommand{\vW}{\boldsymbol{W}}
\newcommand{\val}{{\textrm{value}}}
\newcommand{\Val}{{\textrm{value}}}
\newcommand{\MILP}{{\textrm{MILP}}}
\newcommand{\LP}{{\textrm{LP}}}
\newcommand{\Improve}{\mathrm{Improve}}
\newcommand{\Utility}{\mathrm{SAS}}
\newcommand{\Sol}{\mathrm{Sol}}
\newcommand{\sol}{\mathrm{sol}}
\newcommand{\UB}{\mathrm{UB}}
\newcommand{\LB}{\mathrm{LB}}
\newcommand{\ub}{\mathrm{ub}}
\newcommand{\lb}{\mathrm{lb}}
\newcommand{\B}{\mathrm{B}}
\usepackage{amsmath, amssymb, amsfonts}
\newcommand{\ReLU}{\mathrm{ReLU}}
\newcommand{\CMP}{{\textrm{CMP}}\ }
\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}
\newcommand{\toolname}{Hybrid MILP}

@@

\title{Order reduction and MILP models for real-time DNN robustness certification.}
\date{}

@@

\bibliographystyle{plain} 
\bibliography{references}
\end{document}

>>>>

%\usepackage{times}  % DO NOT CHANGE THIS
%\usepackage{helvet}  % DO NOT CHANGE THIS
%\usepackage{courier}  % DO NOT CHANGE THIS

\usepackage[hyphens]{url}  % DO NOT CHANGE THIS
\usepackage{graphicx} % DO NOT CHANGE THIS

%\urlstyle{rm} % DO NOT CHANGE THIS
%\def\UrlFont{\rm}  % DO NOT CHANGE THIS
%\usepackage{natbib}  % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT

%\usepackage{caption} % DO NOT CHANGE THIS AND DO NOT ADD ANY OPTIONS TO IT
\frenchspacing  % DO NOT CHANGE THIS
%\setlength{\pdfpagewidth}{8.5in} % DO NOT CHANGE THIS
%\setlength{\pdfpageheight}{11in} % DO NOT CHANGE THIS
%
% These are recommended to typeset algorithms but not required. See the subsubsection on algorithms. Remove them if you don't have algorithms in your paper.

\usepackage{algorithm}
\usepackage{algorithmic}
\pagestyle{plain}
\usepackage{threeparttable}
\input{math_commands.tex}
\usepackage{lineno}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{cases}
\captionsetup{compatibility=false}
\usepackage{epstopdf}
\usepackage{placeins}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{calc}
\usepackage{array}
%\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usetikzlibrary{positioning, arrows.meta,calc}
\usepackage{newfloat}
\usepackage{listings}
\DeclareCaptionStyle{ruled}{labelfont=normalfont,labelsep=colon,strut=off} % DO NOT CHANGE THIS
\lstset{%
	basicstyle={\footnotesize\ttfamily},% footnotesize acceptable for monospace
	numbers=left,numberstyle=\footnotesize,xleftmargin=2em,% show line numbers, remove this entire line if you don't want the numbers.
	aboveskip=0pt,belowskip=0pt,%
	showstringspaces=false,tabsize=2,breaklines=true}
\floatstyle{ruled}
\newfloat{listing}{tb}{lst}{}
\floatname{listing}{Listing}
%\newtheorem{proposition}{Proposition}
%\newtheorem{definition}{Definition}
\newcommand{\vW}{\boldsymbol{W}}
\newcommand{\val}{{\textrm{value}}}
\newcommand{\Val}{{\textrm{value}}}
\newcommand{\MILP}{{\textrm{MILP}}}
\newcommand{\LP}{{\textrm{LP}}}
\newcommand{\Improve}{\mathrm{Improve}}
\newcommand{\Utility}{\mathrm{SAS}}
\newcommand{\Sol}{\mathrm{Sol}}
\newcommand{\sol}{\mathrm{sol}}
\newcommand{\UB}{\mathrm{UB}}
\newcommand{\LB}{\mathrm{LB}}
\newcommand{\ub}{\mathrm{ub}}
\newcommand{\lb}{\mathrm{lb}}
\newcommand{\B}{\mathrm{B}}
\usepackage{amsmath, amssymb, amsfonts}
\newcommand{\ReLU}{\mathrm{ReLU}}
\newcommand{\CMP}{{\textrm{CMP}}\ }
\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}
\newcommand{\toolname}{Hybrid MILP}

@@

\title{{\em Global} MILP models and PCA for \\ {\em real-time} DNN robustness certification}
\date{}

@@

\bibliographystyle{splncs04}
\bibliography{references}
\end{document}

### 2025-11-15 CAV 2026/abstract.tex
abstract and title

Deep neural networks (DNNs) are often brittle to small perturbations, leading to extensive research into methods to verify their robustness. Most existing methods focus on local robustness, i.e., the model's behavior in the neighborhood of a specific input. While local robustness enables to evaluate how often non-robust images appear in a large dataset (e.g., by repeating the verification on 1000 pre-obtained images), it fails to provide guarantees on whether new specific incoming inputs are robust, e.g., real-time images in a video stream. Moreover, most verification techniques are computationally intensive, rendering them impractical for real-time deployment on embedded systems.

In this paper, we consider {\em global} robustness, that is, guarantees not restricted to a set of local images. We focus on deriving {\em bounds} on the variation of output values across different decision classes of a DNN under a given perturbation. This global verification problem is significantly more complex than local robustness, as the number of variables doubles (from the deviation image to the image and its deviation). Further, the values each neuron can take are no longer limited to a small neighborhood. To obtain usable bounds, we develop several novel  MILP models for global robustness, with different trade-offs. Last, we use order reduction techniques to reduce the space of inputs considered, avoiding unrealistic images, by using principal component analysis (PCA). These bounds ensure the {\em real-time} certification of robustness for $86\%$ of incoming images in the MNIST benchmark for an $L_1$-perturbation of $.5$, as well as faitfhulness of a surrogate computing the 
%latent
plastic strain due to the deformation of a pipe.

>>>>

Deep neural networks (DNNs) are often brittle to small perturbations, leading to extensive research into methods to verify their robustness. Most existing methods focus on {\em local} robustness, i.e., the model's behavior in the neighborhood of a specific input. Local robustness does {\em not} provide guarantees on whether new specific incoming inputs are robust, e.g., real-time images in a video stream. Moreover, most verification techniques are computationally intensive, rendering them impractical for real-time deployment on embedded systems.

In this paper, we consider {\em global} robustness, which is significantly more complex than local robustness, as %the number of variables doubles (from the deviation image to the image and its deviation). Further, 
the values each neuron can take are no longer limited to a small neighborhood. 
%, that is, guarantees not restricted to a set of local images. 
We focus on deriving {\em bounds} on the variation of output values across different decision classes of a DNN, given $L_\infty$- {\em and} $L_1$-perturbations. To obtain usable bounds, we develop {\em global}  MILP models for global robustness, more efficient than the classical encoding and its variants. Last, we reduce the space dimension, focusing on realistic images, by using principal component analysis (PCA). These bounds ensure the {\em real-time} certification of robustness for $69\%$ (resp. $86\%$) of incoming images for an $L_1$-perturbation of $1$ (resp. $.5$), adding only $0.0005s$ of latency using a single CPU core.
